### 2023-06-11 Notes/paper_notes.tex
Added start of paper notes.

\documentclass{article}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\title{Fair Decision Making}
\author{David Yang, Selena She, Amy Feng, Xander Goslin}
\date{Summer 2023}

\begin{document}

\maketitle

\section{Background Reading}
\subsection{\href{https://arxiv.org/abs/1406.2661}{Generative Adversarial Networks}}

\begin{definition}[Generator]
A \textbf{generator} is a neural network that learns to generate realistic samples by transforming random noise into data samples that resemble the training data.
\end{definition}

\begin{definition}[Discriminator]
A \textbf{discriminator} is a neural network that aims to distinguish between real and fake examples.
\end{definition}

More formally, a generative model captures the data distribution and a discriminative model estimates the probability that a sample came from the training data rather than G. "The generative model can be thought of as analogous to a team of counterfeiters, trying to produce fake currency and use it without detection, while the discriminative model is analogous to the police, trying to detect the counterfeit currency."

\begin{definition}
\textbf{Adversarial nets} refer to the specific case where the generative model generates samples by passing random noise through a multilayer perceptron, and the discriminative model is also a multilayer perceptron. 
\end{definition}

\subsection{\href{https://arxiv.org/abs/2006.11239}{Denoising Diffusion Probabilistic Model} / \href{https://arxiv.org/abs/2010.02502}{Denoising Diffusion Implicit Model}}
\end{document}

### 2023-06-12 Notes/paper_notes.tex
Updated paper notes.

@@
 \usepackage{xcolor}
+\usepackage[symbol]{footmisc}
+
+\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
 
@@
 \title{Fair Decision Making}
-\author{David Yang, Selena She, Amy Feng, Xander Goslin}
+\author{David Yang$^{\dagger}$, Selena She$^{\dagger}$, Amy Feng$^{\dagger}$, Xander Goslin$^{\dagger}$}
 \date{Summer 2023}
@@
 \maketitle
+
+\begin{center}
+    Note: $\dagger$ denotes equal contribution.
+\end{center}
 
@@
 
-\begin{definition}
+\begin{definition}[Adversarial Nets]
 \textbf{Adversarial nets} refer to the specific case where the generative model generates samples by passing random noise through a multilayer perceptron, and the discriminative model is also a multilayer perceptron.
@@
 \subsection{\href{https://arxiv.org/abs/2006.11239}{Denoising Diffusion Probabilistic Model} / \href{https://arxiv.org/abs/2010.02502}{Denoising Diffusion Implicit Model}}
+
+\textit{Other Relevant Resource(s):} \href{https://strikingloo.github.io/wiki/ddim#:~:text=Properties%20of%20DDIM%20vs%20DDPM,have%20similar%20high%2Dlevel%20features}{DDIM vs DDPM Article}
+
+\begin{definition}[Diffusion Model]
+A \textbf{diffusion (probabilistic) model} is a parameterized Markov chain trained using variational inference to produce samples matching the data after finite time.  
+\end{definition}
+
+DDPMs are types of generative models that use probabilistic processes to transform the data from a simple distribution to a more complex target distribution.
+It iteratively refines the initial random distribution, where in each step it removes the noise from the data and eventually ends up creating a realistic sample of data.
+In comparison to Generative Adversarial Nets (GANs), GANs may suffer from \textbf{real mode collapse} in which the generator produces just a small variety of data that is not as diverse as real-world data.
+On the other hand, diffusion models will not have this problem but may take longer/tend to be more computationally expensive.
+\\
+
+\begin{definition}[DDIM]
+A Denoising diffusion implicit model (DDIM) is a more efficient class of iterative implicit probabilistic models with the same training procedure as DDPMs.
+\end{definition}
+
+The generative process of a DDPM is defined as the "reverse of a Markovian diffusion process," which approximates the reverse of the forward diffusion process (from data to noise) and is much slower than a GAN, which typically requires only one pass through a network.
+On the other hand, a DDIM allows for much faster sampling while keeping an equivalent training objective, so that generative models using this architecture are competitive to GANs at the same model size/sample quality." This is done by "estimating the addition of multiple Markov chain jumps by estimating the sum of Gaussian Markov jumps as Gaussian." This generalizes the Markovian forward diffusion process of DDPMs to a non-Markovian one.
+\\
+
+One of the key differences between the DDIM and DDPMs is the "\textbf{consistency}" property (present in DDIMs but not DDPMs): if we start with the same initial latent variable and generate several samples with Markov chains of various lengths, these samples would have similar high-level features.
+The consistency of DDIMs allow for meaningful image interpolation.
+\subsection{\href{https://arxiv.org/abs/2302.10893}{Fair Diffusion: Instructing Text-to-Image Generation Models on Fairness}}
+
+\textbf{Fair Diffusion} is a strategy that attenuates biases after the deployment of generative text-to-image models.
+It shifts a bias, based on human instructions, in any direction yielding arbitrary proportions (e.g.
+identity groups).
+% \includegraphics[]{
+
+% }
 \end{document}

### 2023-06-13 Notes/main.tex
Added notes.

\documentclass[12pt]{amsart}
\usepackage[symbol]{footmisc}
\usepackage{float}

\usepackage{style_template}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

% \newtheorem{theorem}{Theorem}
% \newtheorem{definition}{Definition}

\title{Fair Decision Making}
\author{David Yang$^{\dagger}$, Selena She$^{\dagger}$, Amy Feng$^{\dagger}$, Alexander Goslin$^{\dagger}$}
\date{Summer 2023}

\begin{document}

\maketitle

\begin{center}
    Note: $\dagger$ denotes equal contribution.
\end{center}

\section{General Background Reading}
\subsection{\href{https://arxiv.org/abs/1406.2661}{Generative Adversarial Networks}}

\begin{definition}[Generator]
A \textbf{generator} is a neural network that learns to generate realistic samples by transforming random noise into data samples that resemble the training data.
\end{definition}

\begin{definition}[Discriminator]
A \textbf{discriminator} is a neural network that aims to distinguish between real and fake examples.
\end{definition}

More formally, a generative model captures the data distribution and a discriminative model estimates the probability that a sample came from the training data rather than G. "The generative model can be thought of as analogous to a team of counterfeiters, trying to produce fake currency and use it without detection, while the discriminative model is analogous to the police, trying to detect the counterfeit currency."

\begin{definition}[Adversarial Nets]
\textbf{Adversarial nets} refer to the specific case where the generative model generates samples by passing random noise through a multilayer perceptron, and the discriminative model is also a multilayer perceptron. 
\end{definition}

\vspace{0.5cm}

\subsection{\href{https://arxiv.org/abs/2006.11239}{Denoising Diffusion Probabilistic Model} / \href{https://arxiv.org/abs/2010.02502}{Denoising Diffusion Implicit Model}}

\textit{Other Relevant Resource(s):} \href{https://strikingloo.github.io/wiki/ddim#:~:text=Properties%20of%20DDIM%20vs%20DDPM,have%20similar%20high%2Dlevel%20features}{DDIM vs DDPM Article}

\begin{definition}[Diffusion Model]
A \textbf{diffusion (probabilistic) model} is a parameterized Markov chain trained using variational inference to produce samples matching the data after finite time.  
\end{definition}

DDPMs are types of generative models that use probabilistic processes to transform the data from a simple distribution to a more complex target distribution. It iteratively refines the initial random distribution, where in each step it removes the noise from the data and eventually ends up creating a realistic sample of data. In comparison to Generative Adversarial Nets (GANs), GANs may suffer from \textbf{real mode collapse} in which the generator produces just a small variety of data that is not as diverse as real-world data. On the other hand, diffusion models will not have this problem but may take longer/tend to be more computationally expensive. \\

\begin{definition}[DDIM]
A \textbf{Denoising diffusion implicit model (DDIM)} is a more efficient class of iterative implicit probabilistic models with the same training procedure as DDPMs.
\end{definition}

The generative process of a DDPM is defined as the ``reverse of a Markovian diffusion process," which approximates the reverse of the forward diffusion process (from data to noise) and is much slower than a GAN, which typically requires only one pass through a network. On the other hand, a DDIM allows for much faster sampling while keeping an equivalent training objective, so that generative models using this architecture are competitive to GANs at the same model size/sample quality." This is done by ``estimating the addition of multiple Markov chain jumps by estimating the sum of Gaussian Markov jumps as Gaussian." This generalizes the Markovian forward diffusion process of DDPMs to a non-Markovian one. \\

One of the key differences between the DDIM and DDPMs is the ``\textbf{consistency}" property (present in DDIMs but not DDPMs): if we start with the same initial latent variable and generate several samples with Markov chains of various lengths, these samples would have similar high-level features. The consistency of DDIMs allow for meaningful image interpolation.

\subsection{\href{https://arxiv.org/pdf/2211.05617.pdf}{Debiasing Methods for Fairer Neural Models in Vision and Language Research: A Survey}}

\begin{definition}[Fairness]
\textbf{Fairness} refers to the ``absence of any prejudice or favoritism toward an individual or a group based on their inherent or acquired characteristics."
\end{definition}

\begin{definition}[Bias]
\textbf{Bias} is any unintended behavior resulting from correlation-based processing that ignores further context not explicit in the data.
\end{definition}

Different types of bias include \textbf{inductive bias} (unavoidable bias inherent to the learning task), \textbf{data bias} (bias of representation/sampling/measurement of data towards a group of subjects) and \textbf{intersectional bias} (when an underprivileged group defined by a combination of sensitive attribute and  dynamics of individuals are considerably distinct than when considering one sensitive attribute at a time). \\

We can test the embedding of a given prompt for bias to measure bias in language models. Metrics to measure bias include \href{https://arxiv.org/pdf/1607.06520.pdf}{\textbf{Direct Bias (DB)}}, where we measure the bias as a projection onto a gender subspace, the \href{https://purehost.bath.ac.uk/ws/portalfiles/portal/168480066/CaliskanEtAl_authors_full.pdf}{\textbf{Word Embedding Association Test (WEAT)}} which measures bias through permutation of two sets of target words and two sets of attribute words (e.g. engineers/nurses and male/female). The \href{https://arxiv.org/pdf/1903.10561.pdf}{\textbf{Sentence Embedding Association Test (SEAT)}} is similar to WEAT but works for contextualized word embeddings. \\

\begin{definition}[Existing Debiasing Categorization]
Debiasing approaches are typically divided into three categories: \textbf{preprocessing} (transform the data so that the underlying
discrimination is removed), \textbf{inprocessing} (modify and change state-of-the-art learning
algorithms in order to remove discrimination during the model training process), and \textbf{postprocessing} (performed after training).
\end{definition}

\textit{Note: we anticipate that our approaches will be of the postprocessing type.} \\

The survey paper introduces a new taxonomy to categorize debiasing methods:

\begin{definition}[New Taxonomy for Debiasing Methods]
A \textbf{distributional} strategy modifies the dataset prior to training. \\

An \textbf{inferential} strategy that addresses the problem of fairness based on the model outputs, i.e. that discover and remove social biases without requiring further weight optimization or dataset manipulation
\end{definition}

\newpage

\section{Focused Readings}
\subsection{\href{https://arxiv.org/abs/2302.10893}{Fair Diffusion: Instructing Text-to-Image Generation Models on Fairness}}

\begin{approach*}
\textbf{Fair Diffusion} is a strategy that attenuates biases after the deployment of generative text-to-image models. It shifts a bias, based on human instructions, in any direction yielding arbitrary proportions (e.g. identity groups), by instructing a pre-trained model on fairness during the deployment stage.
\end{approach*}

Fair Diffusion is evaluated with Hugging Face's \href{https://huggingface.co/docs/diffusers/api/pipelines/semantic_stable_diffusion}{Semantic Guidance} pipeline, which allows for changes to image generation to be more easily controlled (and thus enable it to stay closer to the original image composition). \\

For example, consider the following pairs of images, generated with stable diffusion and fair diffusion:

\setlength\intextsep{0pt}{
\begin{figure}[H]
    \centering
\includegraphics[scale = 0.45]{FairDiffusion_BeforeAndAfter.png}\label{fig:fairdiffusion_comparison}
\end{figure}}

We notice that, despite correcting for the protected attribute of gender, the remainder of the generated images' characteristics stay the same.

\begin{figure}[H]
    \centering
\includegraphics[scale = 0.7]{FairDiffusion_Method.png}
    \label{fig:fairdiffusion_method}
\end{figure}

As discussed in the paper, fair diffusion works at the following high-level manner: the generated image $x$ satisfies
\[ x = \eta(p, \gamma(e, s_e)).\]

More specifically, $\eta$ is a function of the text input prompt $p$ (e.g., "A photo of a firefighter") with "fair guidance"
, $\gamma$, given during the generation. In turn, $\gamma$ depends on additional textual descriptions of attribute expressions $e_i$, scaled by $s_{e_i}$ with guidance direction. As a result, the image generation is guided towards the input prompt p
and fairness instructions $e_i$ simultaneously. \\

To realize the different expressions of an attribute with Fair
Diffusion, the authors control the guidance direction by randomly sampling from a desired probability distribution P. That
means each $e_i$ is either increased or decreased depending on the expression that should be promoted/suppressed. \\

The above figure displays a binary case  where concept $e_1$ is promoted (+) and $e_2$ is suppressed (-) during the image
generation -- their direction can be changed based on P. The purpose of the \textbf{lookup table} is to identify prompts requiring fair guidance and to align the output with the users’ fairness notions.

\noindent\rule{\textwidth}{1pt}

\vspace{0.5cm}
Another area this paper investigates is ``bias inspection" in the components of the well-known text-to-image generation model \href{https://huggingface.co/blog/stable_diffusion}{Stable Diffusion}. Stable Diffusion relies on the large-scale image dataset LAION-5B and the pre-trained text encoder model \href{https://huggingface.co/docs/transformers/model_doc/clip#transformers.CLIPTextModel}{CLIP}. \\

In the subset of the image dataset LAION-5B that the paper uses, they found that the ``Science" and ``Engineering" subsets have lower rates of female-appearing persons (around 0.35 and 0.2, respectively), while ``Arts" and ``Caregiving" (around 0.55 and 0.75, respectively) have higher rates of female-appearing persons, reflecting stereotypical gender occupation biases. \\

Similar biases are revealed after the authors use the iEAT Bias Test for CLIP: \\

\begin{figure}[H]
    \centering
\includegraphics[scale = 0.6]{FairDiffusion_CLIP_Bias.png}
    \label{fig:clip_bias}
\end{figure}
In fact, bias amplification occurs when the association is modified by ethnic attributes (males as European and females as African-American). \\

To summarize the results, the authors ``found biases and unfairness in each component of the SD pipeline: in the LAION-5B dataset, in the CLIP encoder, and in the generated images. At the same time, the biases are not simply mirrored between LAION-5B and SD’s outcome and do not show a clear tendency."

\begin{discussion*}
The prompts in this paper are all of the format ``give me a photo of the face of a [ ]." \\

A specific ambiguous case mentioned is the ``face of a dishwasher” (which gives a photo of a dishwasher rather than someone washing the dishes). Consequently, can the given prompt be modified to ``the face of a person washing dishes" (or other similar formats), and how might these shifts affect the paper's results?
\end{discussion*}

\begin{extension*}
Implicit associations are not accounted for (this paper requires a lookup table mapping pre-defined occupations to protected groups). However, a prompt such as “a photo of a hospital” may generate images where doctors are predominately male. \\

\noindent \textbf{Can we extend or modify the existing work to support biases implied from text prompts?} 
\end{extension*}

\end{document}

### 2023-06-14 Notes/main.tex
Day 9 Notes added.

@@
 
+There is also a distinction between methods that focus on optimization via training into two categories:
+\begin{definition}[1-Step and 2-Step Training]
+\textbf{One-step-training} includes fair models generated for a particular task via a single optimization procedure, whereas \textbf{Two-step-training} includes models where a new training phase must be performed to fix an existing biased model.
+\end{definition}
+
+There a few methods to debias one-step-training models:
+\begin{definition}[Groups of One-Step-Learning Debiasing Methods]
+\textbf{Adversarial} methods use adversarial examples to teach the model not to resort to undesired biases. \\
+
+\textbf{Causal} methods leverage knowledge on causal-effect between protected attributes and outcomes to fix model unfairness (e.g.
+create new examples during training/generate ``counterfactual samples").
+\\
+
+\textbf{Disentanglement} methods break down features in latent space to manipulate information independently. \\
+
+\textbf{Optimization} methods include loss function adaptions, the addition of regularization terms, and other modifications for improving weight optimization. 
+\end{definition}
+
+\begin{discussion*}
+Of the four one-step-learning debiasing methods discussed above, we anticipate looking at \textbf{Adversarial} methods and \textbf{Disentanglement} methods. \\
+
+An adversarial approach may work similarly to in the following \href{https://arxiv.org/pdf/2203.11933.pdf}{Adversarial Learning Debiasing Method} paper, and a related-to-disentanglement approach is discussed in this \href{https://arxiv.org/pdf/2302.00070.pdf}{Debiasing VLMs via Biased Prompts} paper (that being said, this approach may be better categorized as \textbf{Vector-Space Manipulation}, which is described later).
+\end{discussion*}
+
+Inferential models are distinct from distributional models since they intervene during \textit{inference time} (post-training) to make models fairer.
+
+\begin{definition}[Inferential Models]
+\textbf{Prompting} prepends or alters the model input with specific triggers that stimulate a bias-free result. \\
+
+\textbf{Vector-Space Manipulation} manipulates the embedding space to remove undesired biases.
+\end{definition}
+
+\begin{discussion*}
+We've already seen these two approaches (prompting and vector-space manipulation) in other papers; specifically, the Fair Diffusion (\ref{fairdiffusion}) paper is an example of a prompting approach whereas the Debiasing VLMs paper (\ref{embedding}) paper takes a vector-space manipulation approach.
+\end{discussion*}
+
 \newpage
@@
 \section{Focused Readings}
-\subsection{\href{https://arxiv.org/abs/2302.10893}{Fair Diffusion: Instructing Text-to-Image Generation Models on Fairness}}
+\subsection{\href{https://arxiv.org/abs/2302.10893}{Fair Diffusion: Instructing Text-to-Image Generation Models on Fairness}}\label{fairdiffusion}
 
@@
 Fair Diffusion is evaluated with Hugging Face's \href{https://huggingface.co/docs/diffusers/api/pipelines/semantic_stable_diffusion}{Semantic Guidance} pipeline, which allows for changes to image generation to be more easily controlled (and thus enable it to stay closer to the original image composition).
-\\
+To classify the gender of the generated images, they use the pre-trained \href{https://arxiv.org/pdf/1908.04913.pdf}{FairFace classifier}.\\
 
@@
 We notice that, despite correcting for the protected attribute of gender, the remainder of the generated images' characteristics stay the same. 
-
 \begin{figure}[H]
     \centering
-\includegraphics[scale = 0.7]{FairDiffusion_Method.png}
+\includegraphics[scale = 0.65]{FairDiffusion_Method.png}
     \label{fig:fairdiffusion_method}
@@
 
+\newpage
+
+\subsection{\href{https://arxiv.org/pdf/2302.00070.pdf}{Debiasing Vision-Language Models via Biased Prompts}}\label{embedding}
+
+\begin{approach*}
+Many approaches for debiasing Vision-Language Models require training or fine-tuning models using resampled datasets, or modified objectives, which can be computationally expensive.
+The paper proposes a general approach for "self-debiasing foundation vision-language models by projecting out biased directions in the text embedding." \\
+
+This approach creates a projection matrix (where each row is an attribute) that projects out biased directions.
+To address possible unstabilities caused by prompts defining the biased directions, they use ``positive pairs" (pairs of prompts that are expected to have the same semantic meaning after projection) to calibrate the projection matrix.
+Their overall approach does not require training, data, or labels, so it is computationally efficient.
+\end{approach*}
+
+The bias of a classifier will be quantified by computing the cosine similarity between its weights and the corresponding spurious feature.
+We expect rows of classifier weights to have similar cosine similarities to pairs of embeddings: for example, the embedding of ``a photo of a doctor" should be similar to ``a photo of a male doctor" and ``a photo of a female doctor."
+
+\begin{approach*}
+To evaluate generative models, the paper uses the CLIP classifier to predict the sensitive attributes and human evaluation to corroborate these results. \\
+
+They mention that as an alternative, the FairFace classifier could be used.
+However, they note that the ``domain shift between the FairFace dataset and the generated images significantly impaired performance" and thus used the CLIP classifier.
+\end{approach*}
+
+\begin{discussion*}
+This paper mentions that FairFace dataset and the generated images significantly impacts the bias/general performance (so they used CLIP) but the Diffusion Paper (\ref{fairdiffusion}) used FairFace as the final classifier.
+\\
+
+We will need to be cognizant of our choice, specifically how the classifiers work on our generated images.
+\end{discussion*}
+
+\newpage
+
+\subsection{\href{https://arxiv.org/pdf/2103.00020.pdf}{Learning Transferable Visual Models from Natural Language Supervision (CLIP)}}
+
+\begin{approach*} \textbf{CLIP} (Contrastive Language-Image Pre-training), is an efficient method of learning from natural language supervision. \\
+
+Given a batch of $N$ (image, text) pairs, CLIP is trained to predict which of the $N \times N$ possible (image, text) pairings across a batch occurred.
+They do this by jointly training an image encoder and text encoder to maximize the cosine similarity of the image and text embeddings of the N real pairs in the batch.
+\end{approach*}
 \end{document}

### 2023-06-16 Notes/meeting_notes.tex
Added Meeting Notes.

\documentclass[12pt]{amsart}
\usepackage[symbol]{footmisc}
\usepackage{float}

\usepackage{style_template}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

% \newtheorem{theorem}{Theorem}
% \newtheorem{definition}{Definition}

\title{UMD Fairness Research Group Meeting Notes}
\author{David Yang$^{\dagger}$, Selena She$^{\dagger}$, Amy Feng$^{\dagger}$, Alexander Goslin$^{\dagger}$}
\date{Summer 2023}

\begin{document}

\maketitle

\begin{center}
    Note: $\dagger$ denotes equal contribution.
\end{center}

\section{Bilevel Optimization Problems in ML and Efficient Solvers (June 15th)}

\textit{Led by Mucong Ding.} \\

\begin{definition}[Bilevel Optimization]
The \textbf{Bilevel Optimization} problem is 
\[\min_{v, \theta} f(v, \theta) \, \text{   s.t.  } \, \theta \in \underset{\theta'}{\mathrm{argmin}} \, \, g(v, \theta’)\]

\noindent where $\underset{v, \theta}\min f(v, \theta)$ is the \textbf{outer function} and $\theta \in \underset{\theta'}{\mathrm{argmin}} \, \, g(v, \theta’)$ is the \textbf{inner function}.
\end{definition}

Note that the bilevel optimization problem can even be framed as a hyperparameter tuning problem in Machine Learning. The bilevel optimization problem can also be summarized as solving two interdependent problems where the outer problem depends on the inner problem. \\

Bilevel Optimization Problems in Machine Learning include the following:
\begin{enumerate}
    \item \textbf{Dataset Condensation/Distillation}: we want to learn a synthetic dataset such that the model trained on it has comparable performance to the model trained on the original dataset.
    \item \textbf{Coreset Selection}: similar to Dataset Condensation, but the learnable set is a subset of the original training set.
    \item \textbf{Targeted Dataset Poisoning}: modify the training data to cause reclassification of the unmodified test image.
    \item \textbf{Learnable Dataset Augmentation}: the learning of dataset augmentation can be formulated to minimize the loss of the trained model on the validation split.
\end{enumerate}

\begin{definition}[Efficient Solvers]BO problems that enjoy convergence guarantee under mild conditions are \textbf{exact solvers}. The main approaches include Hypergradient descent methods, stationary, seeking methods, and value-function methods.
\end{definition}

To summarize, Bilevel Optimization arises in many ML problems, each of which have unique setups and characteristics.

\end{document}

### 2023-06-16 Notes/paper_notes.tex
Added Meeting Notes.

@@
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{graphics}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{listings}
-\usepackage{mathtools}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\usepackage{xcolor}
+\documentclass[12pt]{amsart}
 \usepackage[symbol]{footmisc}
+\usepackage{float}
 
+\usepackage{style_template}
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
+% \newtheorem{theorem}{Theorem}
+% \newtheorem{definition}{Definition}
 
 \title{Fair Decision Making}
-\author{David Yang$^{\dagger}$, Selena She$^{\dagger}$, Amy Feng$^{\dagger}$, Xander Goslin$^{\dagger}$}
+\author{David Yang$^{\dagger}$, Selena She$^{\dagger}$, Amy Feng$^{\dagger}$, Alexander Goslin$^{\dagger}$}
 \date{Summer 2023}
@@
 
-\section{Background Reading}
+\section{General Background Reading}
 \subsection{\href{https://arxiv.org/abs/1406.2661}{Generative Adversarial Networks}}
@@
 
+\vspace{0.5cm}
+
 \subsection{\href{https://arxiv.org/abs/2006.11239}{Denoising Diffusion Probabilistic Model} / \href{https://arxiv.org/abs/2010.02502}{Denoising Diffusion Implicit Model}}
@@
 \begin{definition}[DDIM]
-A Denoising diffusion implicit model (DDIM) is a more efficient class of iterative implicit probabilistic models with the same training procedure as DDPMs.
+A \textbf{Denoising diffusion implicit model (DDIM)} is a more efficient class of iterative implicit probabilistic models with the same training procedure as DDPMs.
 \end{definition}
 
-The generative process of a DDPM is defined as the "reverse of a Markovian diffusion process," which approximates the reverse of the forward diffusion process (from data to noise) and is much slower than a GAN, which typically requires only one pass through a network.
-On the other hand, a DDIM allows for much faster sampling while keeping an equivalent training objective, so that generative models using this architecture are competitive to GANs at the same model size/sample quality." This is done by "estimating the addition of multiple Markov chain jumps by estimating the sum of Gaussian Markov jumps as Gaussian." This generalizes the Markovian forward diffusion process of DDPMs to a non-Markovian one.
+The generative process of a DDPM is defined as the ``reverse of a Markovian diffusion process," which approximates the reverse of the forward diffusion process (from data to noise) and is much slower than a GAN, which typically requires only one pass through a network.
+On the other hand, a DDIM allows for much faster sampling while keeping an equivalent training objective, so that generative models using this architecture are competitive to GANs at the same model size/sample quality." This is done by ``estimating the addition of multiple Markov chain jumps by estimating the sum of Gaussian Markov jumps as Gaussian." This generalizes the Markovian forward diffusion process of DDPMs to a non-Markovian one.
 \\
 
-One of the key differences between the DDIM and DDPMs is the "\textbf{consistency}" property (present in DDIMs but not DDPMs): if we start with the same initial latent variable and generate several samples with Markov chains of various lengths, these samples would have similar high-level features.
+One of the key differences between the DDIM and DDPMs is the ``\textbf{consistency}" property (present in DDIMs but not DDPMs): if we start with the same initial latent variable and generate several samples with Markov chains of various lengths, these samples would have similar high-level features.
 The consistency of DDIMs allow for meaningful image interpolation.
-\subsection{\href{https://arxiv.org/abs/2302.10893}{Fair Diffusion: Instructing Text-to-Image Generation Models on Fairness}}
 
+\subsection{\href{https://arxiv.org/pdf/2211.05617.pdf}{Debiasing Methods for Fairer Neural Models in Vision and Language Research: A Survey}}
+
+\begin{definition}[Fairness]
+\textbf{Fairness} refers to the ``absence of any prejudice or favoritism toward an individual or a group based on their inherent or acquired characteristics."
+\end{definition}
+
+\begin{definition}[Bias]
+\textbf{Bias} is any unintended behavior resulting from correlation-based processing that ignores further context not explicit in the data.
+\end{definition}
+
+Different types of bias include \textbf{inductive bias} (unavoidable bias inherent to the learning task), \textbf{data bias} (bias of representation/sampling/measurement of data towards a group of subjects) and \textbf{intersectional bias} (when an underprivileged group defined by a combination of sensitive attribute and  dynamics of individuals are considerably distinct than when considering one sensitive attribute at a time).
+\\
+
+We can test the embedding of a given prompt for bias to measure bias in language models.
+Metrics to measure bias include \href{https://arxiv.org/pdf/1607.06520.pdf}{\textbf{Direct Bias (DB)}}, where we measure the bias as a projection onto a gender subspace, the \href{https://purehost.bath.ac.uk/ws/portalfiles/portal/168480066/CaliskanEtAl_authors_full.pdf}{\textbf{Word Embedding Association Test (WEAT)}} which measures bias through permutation of two sets of target words and two sets of attribute words (e.g.
+engineers/nurses and male/female).
+The \href{https://arxiv.org/pdf/1903.10561.pdf}{\textbf{Sentence Embedding Association Test (SEAT)}} is similar to WEAT but works for contextualized word embeddings.
+\\
+
+\begin{definition}[Existing Debiasing Categorization]
+Debiasing approaches are typically divided into three categories: \textbf{preprocessing} (transform the data so that the underlying
+discrimination is removed), \textbf{inprocessing} (modify and change state-of-the-art learning
+algorithms in order to remove discrimination during the model training process), and \textbf{postprocessing} (performed after training).
+\end{definition}
+
+\textit{Note: we anticipate that our approaches will be of the postprocessing type.} \\
+
+The survey paper introduces a new taxonomy to categorize debiasing methods:
+
+\begin{definition}[New Taxonomy for Debiasing Methods]
+A \textbf{distributional} strategy modifies the dataset prior to training. \\
+
+An \textbf{inferential} strategy that addresses the problem of fairness based on the model outputs, i.e.
+that discover and remove social biases without requiring further weight optimization or dataset manipulation
+\end{definition}
+
+There is also a distinction between methods that focus on optimization via training into two categories:
+\begin{definition}[1-Step and 2-Step Training]
+\textbf{One-step-training} includes fair models generated for a particular task via a single optimization procedure, whereas \textbf{Two-step-training} includes models where a new training phase must be performed to fix an existing biased model.
+\end{definition}
+
+There a few methods to debias one-step-training models:
+\begin{definition}[Groups of One-Step-Learning Debiasing Methods]
+\textbf{Adversarial} methods use adversarial examples to teach the model not to resort to undesired biases. \\
+
+\textbf{Causal} methods leverage knowledge on causal-effect between protected attributes and outcomes to fix model unfairness (e.g.
+create new examples during training/generate ``counterfactual samples").
+\\
+
+\textbf{Disentanglement} methods break down features in latent space to manipulate information independently. \\
+
+\textbf{Optimization} methods include loss function adaptions, the addition of regularization terms, and other modifications for improving weight optimization. 
+\end{definition}
+
+\begin{discussion*}
+Of the four one-step-learning debiasing methods discussed above, we anticipate looking at \textbf{Adversarial} methods and \textbf{Disentanglement} methods. \\
+
+An adversarial approach may work similarly to in the following \href{https://arxiv.org/pdf/2203.11933.pdf}{Adversarial Learning Debiasing Method} paper, and a related-to-disentanglement approach is discussed in this \href{https://arxiv.org/pdf/2302.00070.pdf}{Debiasing VLMs via Biased Prompts} paper (that being said, this approach may be better categorized as \textbf{Vector-Space Manipulation}, which is described later).
+\end{discussion*}
+
+Inferential models are distinct from distributional models since they intervene during \textit{inference time} (post-training) to make models fairer.
+
+\begin{definition}[Inferential Models]
+\textbf{Prompting} prepends or alters the model input with specific triggers that stimulate a bias-free result. \\
+
+\textbf{Vector-Space Manipulation} manipulates the embedding space to remove undesired biases.
+\end{definition}
+
+\begin{discussion*}
+We've already seen these two approaches (prompting and vector-space manipulation) in other papers; specifically, the Fair Diffusion (\ref{fairdiffusion}) paper is an example of a prompting approach whereas the Debiasing VLMs paper (\ref{embedding}) paper takes a vector-space manipulation approach.
+\end{discussion*}
+
+\newpage
+
+\section{Focused Readings}
+\subsection{\href{https://arxiv.org/abs/2302.10893}{Fair Diffusion: Instructing Text-to-Image Generation Models on Fairness}}\label{fairdiffusion}
+
+\begin{approach*}
 \textbf{Fair Diffusion} is a strategy that attenuates biases after the deployment of generative text-to-image models.
 It shifts a bias, based on human instructions, in any direction yielding arbitrary proportions (e.g.
-identity groups).
-% \includegraphics[]{
+identity groups), by instructing a pre-trained model on fairness during the deployment stage.
+\end{approach*}
 
-% }
+Fair Diffusion is evaluated with Hugging Face's \href{https://huggingface.co/docs/diffusers/api/pipelines/semantic_stable_diffusion}{Semantic Guidance} pipeline, which allows for changes to image generation to be more easily controlled (and thus enable it to stay closer to the original image composition).
+To classify the gender of the generated images, they use the pre-trained \href{https://arxiv.org/pdf/1908.04913.pdf}{FairFace classifier}.\\
+
+For example, consider the following pairs of images, generated with stable diffusion and fair diffusion:
+
+\setlength\intextsep{0pt}{
+\begin{figure}[H]
+    \centering
+\includegraphics[scale = 0.45]{FairDiffusion_BeforeAndAfter.png}\label{fig:fairdiffusion_comparison}
+\end{figure}}
+
+We notice that, despite correcting for the protected attribute of gender, the remainder of the generated images' characteristics stay the same. 
+\begin{figure}[H]
+    \centering
+\includegraphics[scale = 0.65]{FairDiffusion_Method.png}
+    \label{fig:fairdiffusion_method}
+\end{figure}
+
+As discussed in the paper, fair diffusion works at the following high-level manner: the generated image $x$ satisfies
+\[ x = \eta(p, \gamma(e, s_e)).\]
+
+More specifically, $\eta$ is a function of the text input prompt $p$ (e.g., "A photo of a firefighter") with "fair guidance"
+, $\gamma$, given during the generation.
+In turn, $\gamma$ depends on additional textual descriptions of attribute expressions $e_i$, scaled by $s_{e_i}$ with guidance direction.
+As a result, the image generation is guided towards the input prompt p
+and fairness instructions $e_i$ simultaneously. \\
+
+To realize the different expressions of an attribute with Fair
+Diffusion, the authors control the guidance direction by randomly sampling from a desired probability distribution P. That
+means each $e_i$ is either increased or decreased depending on the expression that should be promoted/suppressed. \\
+
+The above figure displays a binary case  where concept $e_1$ is promoted (+) and $e_2$ is suppressed (-) during the image
+generation -- their direction can be changed based on P.
+The purpose of the \textbf{lookup table} is to identify prompts requiring fair guidance and to align the output with the users’ fairness notions.
+
+\noindent\rule{\textwidth}{1pt}
+
+\vspace{0.5cm}
+Another area this paper investigates is ``bias inspection" in the components of the well-known text-to-image generation model \href{https://huggingface.co/blog/stable_diffusion}{Stable Diffusion}.
+Stable Diffusion relies on the large-scale image dataset LAION-5B and the pre-trained text encoder model \href{https://huggingface.co/docs/transformers/model_doc/clip#transformers.CLIPTextModel}{CLIP}.
+\\
+
+In the subset of the image dataset LAION-5B that the paper uses, they found that the ``Science" and ``Engineering" subsets have lower rates of female-appearing persons (around 0.35 and 0.2, respectively), while ``Arts" and ``Caregiving" (around 0.55 and 0.75, respectively) have higher rates of female-appearing persons, reflecting stereotypical gender occupation biases.
+\\
+
+Similar biases are revealed after the authors use the iEAT Bias Test for CLIP: \\
+
+\begin{figure}[H]
+    \centering
+\includegraphics[scale = 0.6]{FairDiffusion_CLIP_Bias.png}
+    \label{fig:clip_bias}
+\end{figure}
+In fact, bias amplification occurs when the association is modified by ethnic attributes (males as European and females as African-American). \\
+
+To summarize the results, the authors ``found biases and unfairness in each component of the SD pipeline: in the LAION-5B dataset, in the CLIP encoder, and in the generated images.
+At the same time, the biases are not simply mirrored between LAION-5B and SD’s outcome and do not show a clear tendency."
+
+\begin{discussion*}
+The prompts in this paper are all of the format ``give me a photo of the face of a [ ]." \\
+
+A specific ambiguous case mentioned is the ``face of a dishwasher” (which gives a photo of a dishwasher rather than someone washing the dishes).
+Consequently, can the given prompt be modified to ``the face of a person washing dishes" (or other similar formats), and how might these shifts affect the paper's results?
+\end{discussion*}
+
+\begin{extension*}
+Implicit associations are not accounted for (this paper requires a lookup table mapping pre-defined occupations to protected groups).
+However, a prompt such as “a photo of a hospital” may generate images where doctors are predominately male.
+\\
+
+\noindent \textbf{Can we extend or modify the existing work to support biases implied from text prompts?} 
+\end{extension*}
+
+\newpage
+
+\subsection{\href{https://arxiv.org/pdf/2302.00070.pdf}{Debiasing Vision-Language Models via Biased Prompts}}\label{embedding}
+
+\begin{approach*}
+Many approaches for debiasing Vision-Language Models require training or fine-tuning models using resampled datasets, or modified objectives, which can be computationally expensive.
+The paper proposes a general approach for "self-debiasing foundation vision-language models by projecting out biased directions in the text embedding." \\
+
+This approach creates a projection matrix (where each row is an attribute) that projects out biased directions.
+To address possible unstabilities caused by prompts defining the biased directions, they use ``positive pairs" (pairs of prompts that are expected to have the same semantic meaning after projection) to calibrate the projection matrix.
+Their overall approach does not require training, data, or labels, so it is computationally efficient.
+\end{approach*}
+
+The bias of a classifier will be quantified by computing the cosine similarity between its weights and the corresponding spurious feature.
+We expect rows of classifier weights to have similar cosine similarities to pairs of embeddings: for example, the embedding of ``a photo of a doctor" should be similar to ``a photo of a male doctor" and ``a photo of a female doctor."
+
+\begin{approach*}
+To evaluate generative models, the paper uses the CLIP classifier to predict the sensitive attributes and human evaluation to corroborate these results. \\
+
+They mention that as an alternative, the FairFace classifier could be used.
+However, they note that the ``domain shift between the FairFace dataset and the generated images significantly impaired performance" and thus used the CLIP classifier.
+\end{approach*}
+
+\begin{discussion*}
+This paper mentions that FairFace dataset and the generated images significantly impacts the bias/general performance (so they used CLIP) but the Diffusion Paper (\ref{fairdiffusion}) used FairFace as the final classifier.
+\\
+
+We will need to be cognizant of our choice, specifically how the classifiers work on our generated images.
+\end{discussion*}
+
+\newpage
+
+\subsection{\href{https://arxiv.org/pdf/2103.00020.pdf}{Learning Transferable Visual Models from Natural Language Supervision (CLIP)}}
+
+\begin{approach*} \textbf{CLIP} (Contrastive Language-Image Pre-training), is an efficient method of learning from natural language supervision. \\
+
+Given a batch of $N$ (image, text) pairs, CLIP is trained to predict which of the $N \times N$ possible (image, text) pairings across a batch occurred.
+They do this by jointly training an image encoder and text encoder to maximize the cosine similarity of the image and text embeddings of the N real pairs in the batch.
+\end{approach*}
+
+\subsection{\href{https://openreview.net/pdf?id=pd1P2eUBVfq}{Diffusion Models Already Have a Semantic Latent Space}}
+
+\begin{approach*}
+Diffusion models lack a semantic latent space which is essential for controlling the generative process.
+The authors introduce a asymmetric reverse process (Asyrp) which discovers the semantic latent space in frozen pretrained diffusion models.
+The semantic latent space, named h-space, has nice properties to accommodate semantic image manipulation: homogeneity, linearity, robustness, and consistency across timesteps.
+\end{approach*}
+
 \end{document}

### 2023-06-17 Notes/paper_notes.tex
Updated day 12.

@@
 
+\subsection{\href{https://arxiv.org/pdf/2110.02711.pdf}{DiffusionCLIP: Text-Guided Diffusion Models for Robust Image Manipulation}}
+
+\begin{approach*}
+\textbf{DiffusionCLIP} performs text-driven image manipulation using diffusion models. Based on
+full inversion capability and high-quality image generation power of recent diffusion models, the method performs zeroshot image manipulation successfully even between unseen domains.
+The authors propose a novel noise combination
+method that allows straightforward multi-attribute manipulation. Code is available in their
+\href{https://github.com/gwang-kim/DiffusionCLIP.git}{DiffusionCLIP GitHub}
+\end{approach*}
+
+Other ``state-of-the-art text-driven manipulation methods" include TediGAN, StyleCLIP, and \href{https://arxiv.org/pdf/2108.00946.pdf}{StyleGAN-NADA} (which leverages GAN inversion and CLIP loss to achieve image manipulation that does not require additional training with simple text prompts).
+
+\newpage
+
+\section{Summary of Work So Far}
+
+\subsection{Face Detectors}
+
+Existing Facial Detection Algorithms are evaluated on the widely known \href{http://shuoyang1213.me/WIDERFACE/index.html}
+{WIDER FACE} (Face Detection Benchmark Dataset).
+A number of Facial Detection Algorithms and their evaluations on WIDER FACE can be found \href{http://shuoyang1213.me/WIDERFACE/WiderFace_Results.html}{here}.
+Note that some of these algorithms are object detection algorithms adapted for facial recognition, but some are also specifically facial detectors (e.g.
+RetinaFace, YOLO5Face).
+
 \end{document}

### 2023-06-22 Notes/paper_notes.tex
Added some paper notes.

@@
 \begin{approach*}
-\textbf{DiffusionCLIP} performs text-driven image manipulation using diffusion models. Based on
-full inversion capability and high-quality image generation power of recent diffusion models, the method performs zeroshot image manipulation successfully even between unseen domains.
+\textbf{DiffusionCLIP} performs text-driven image manipulation using diffusion models.
+Based on full inversion capability and high-quality image generation power of recent diffusion models, the method performs zeroshot image manipulation successfully even between unseen domains.
 The authors propose a novel noise combination
@@
 Other ``state-of-the-art text-driven manipulation methods" include TediGAN, StyleCLIP, and \href{https://arxiv.org/pdf/2108.00946.pdf}{StyleGAN-NADA} (which leverages GAN inversion and CLIP loss to achieve image manipulation that does not require additional training with simple text prompts).
+
+\subsection{\href{https://hci.stanford.edu/courses/cs335/2020/sp/dimsonthomas_86285_6198916_report.pdf}{Translating from Unfair to Fair Embeddings}}
+
+\begin{approach*}
+Use a translator network (a neural network) to produce an alternative embedding for a given photo.
+The translator network assumes nothing about the structure or training procedure for the original embeddings.
+\\
+
+The overall goal is to preserve as much of the original embedding as possible while removing any encoding of protected attributes.
+\end{approach*}
+
+\begin{discussion*}
+In our own experiments, we can think about their loss function choice (backed up by other work in literature) and their overall procedure.
+\end{discussion*}
 

### 2023-06-29 Notes/meeting_notes.tex
Updated Meeting notes with Jun. 22nd meeting.

@@
 
+\newpage
+
+\section{Upcoming Projects: (Extreme Multi-label Compression/Online Data Pruning/GNNs for Tensor Completion)}
+
+\textit{Led by Tahseen Rabbani.} \\
+
+\begin{definition}[Extreme Multi-label Learning]
+The eXtreme Multi-label Learning (XML) addresses the problem
+of learning a classifier which can automatically tag a data sample
+with the most relevant subset of labels from a large label set. 
+\end{definition}
+
+\textit{Note: the above definition was taken from the following \href{https://arxiv.org/pdf/1704.03718.pdf}{Deep Extreme Multi-label Learning} paper.} \\
+
+Examples of Extreme Multi-label Datasets include ``Delicious'' (200k), Amazon (670k) -- a product to product recommender, and Wiki (500k) -- excerpts of Wikipedia articles. One of the important steps 
+in this direction is to determine how to perform Extreme Multi-label Compression for better ML on these datasets. \\
+
+A conventional compression strategy is described in \href{https://link.springer.com/article/10.1007/s10994-011-5276-1}{Zhou et.
+al (2012): Compressed labeling on distilled labelsets for multi-label learning}.
+A few key weaknesses/observations include:
+\begin{itemize}
+\item The Recovery algorithm $(y*)^{-1}$ restores several classes at once (distillates collates frequently occurring label patterns) all with equal likelihood.
+\item \textbf{We should try to predict a single most likely class/bit in the true label, i.e. P@1.}
+\item SVMS are not appropriate when $p$ (label size) is large. For Delicious-200k, even at a 99\% compression, we would need to train over 200k SVMs over samples with 700k features.
+\item Distillation scheme presented in Zhou et. al will not work for our regime since label size is greater than sample count and there is minimal overlap between labels.
+\end{itemize}
+
+They propose training a DNN over compressed labels. Further observations include:
+``if we believe that round($y^{\ast}$), $y^{\ast}$ is in $R^c$, is close to the SGP (Signed Gaussian Projection) of $y$, then we can find the most likely label $i$ in $y$ by looking at the SGP of the $e_i.$'' \\
+
+Thus, they propose finding the most likely label by comparing only a subset of bits within the SGP of $y$ that were predicted with high accuracy with the equivalent subset in $e_i$. \\
+
+Other topics they are interested in include \textbf{Tensor Completion via GNNs} and \textbf{Better Data Pruning for Large Models}.
+For the latter topic, some motivation includes the fact that ``For large vision transformers, an additional 2 billion pre-training data points (starting from 1 billion) leads to an accuracy gain on ImageNet of a few percentage points.''
+Consequently, there is an observed ``power law" between test-accuracy and the number of examples for large datasets, which can be improved on with better data pruning for large models.
 \end{document}

### 2023-06-30 Notes/meeting_notes.tex
Day 25 added.

@@
 Consequently, there is an observed ``power law" between test-accuracy and the number of examples for large datasets, which can be improved on with better data pruning for large models.
+
+\section{Scene Detection in Vision Language Models}
+
+\textit{Led by Yuancheng Xu.} \\
+
+\textit{Note: since Yuancheng preferred to not have his presentation recorded, I refrained from sharing notes for confidentiality.}
+
+\section{Hyper-Dimensional Function Encoding and its Extensions}
+
+\begin{definition}[Continuous Objects]
+    \textbf{Continuous objects} are objects that can be sampled []. \\
+
+    The sample distribution and resolution may vary between the training and testing phase.
+\end{definition}
+
+Suppose one wants to perform Machine Learning tasks on coninuous objects (regression, classification, continuous object prediction, function-to-function mapping), it would be great to encode a continuous objects into a fixed-length vector (so that it can be passed into something like a Neural Network).
+In practice, the continuous objects will be captured by the samples of them, and so traditional Neural Network methods may not work since input dimensions may change. \\
+
+Let $R$ be the continuous object to encode with $\{x_1, x_2, \dots, x_n\}$ being $n$ i.i.d samples from $R$ (with the samples are drawn from a distribution $p$ i.e.
+$x_i \sim p(R)$ with $p(x) > 0$ for all $x \in \mathbb{R}$).
+We want an encoder $E(\{x_1, \dots, x_n\}) \rightarrow \mathbb{C}^N.$
+
+\begin{itemize}
+    \item \textbf{Fixed-Length Representation}: $E$ maps arbitrarily many samples into fixed length vector.
+    \item \textbf{Sample Invariance}: As $n \rightarrow \infty$, $E(\{x_1, x_2, \dots, x_n\}) \rightarrow V_\infty$ where $V_\infty$ is independent of $p$.
+    \item \textbf{Decodable}: Suppose $z=E(R)$, one can determine $Prob(x \in R)$ purely from $z$.
+\end{itemize}
+
+Previous work includes Support Vector Regression and Vector Function Architecture (mathematical details left out).
+Dehao then presented some methodology on his approach and the differences between his approach and previous ones.
+\\
+
+A high-dimensional experiement found that the performance of an encoding does not depend on the \underline{explicit dimension} $d$, but depends on the \underline{complexity} of the function.
+
+\section{Explaining Embeddings from Model Outputs}
+
+\textit{Led by Bang An.} \\
 \end{document}

### 2023-07-07 Notes/meeting_notes.tex
Added Day 32: notes and blog.

@@
 \textit{Led by Bang An.} \\
+
+\newpage
+
+\section{Source-Free Domain Adaptation}
+
+\textit{Led by Hesun Chen.} \\
+
+Datapoints from different datasets confer different distributions. Distribution Shift
+
+In classic DA, source and target data are referenced at the same time.
+This cross reference may cause privacy leaks, and so a better way is to keep data local.
+Furthermore, frequently referencing data results in heavy communication costs.
+In source-free DA, source and target data are referenced separately (first, models are trained on source domains and then it is passed to the target domain).
+
+Pseudo labeling is important since labeled data becomes inaccessible in later stages.
+Three types of pseudo label methods include hidden structure based, data augmentation based, and knowledge distillation based.
 \end{document}

### 2023-07-07 Notes/paper_notes.tex
Added Day 32: notes and blog.

@@
 Many approaches for debiasing Vision-Language Models require training or fine-tuning models using resampled datasets, or modified objectives, which can be computationally expensive.
-The paper proposes a general approach for "self-debiasing foundation vision-language models by projecting out biased directions in the text embedding." \\
+The paper proposes a general approach for ``self-debiasing foundation vision-language models by projecting out biased directions in the text embedding." \\
 
@@
 
+\subsection{\href{https://arxiv.org/pdf/2303.07345.pdf}{Erasing Concepts from Diffusion Models}}
+
+\begin{approach*}
+``We propose a fine-tuning method that can erase a visual concept from a pre-trained diffusion model, given only the name of the style and using negative guidance as a teacher.
+Unlike previous methods, our approach can remove concepts
+from a diffusion model permanently rather than modifying
+the output at the inference time, so it cannot be circumvented
+even if a user has access to model weights."
+\end{approach*}
+
+\begin{discussion*}
+In our work, it could be beneficial to remove the concept of gender or an association of a specific gender to a profession/occupation.
+For example, we may want to remove the correlation for doctors being predominately male.
+\\
+
+On the other hand, removing the entire concept of gender may lead to deformed images, however, so we must be careful when thinking about the concept we want to erase.
+\end{discussion*}
+
+There are two types of parameters that will be fine-tuned when a concept is to be erased:
+
+\textbf{Cross-attention parameters} serve as a gateway to the prompt and directly depend on the text prompt, while other parameters (such as \textbf{self-attention parameters}) tend to contribute to a visual concept even if the concept is not mentioned in the prompt.
+\\
+
+Fine-tuning is done on the cross attentions,
+ESD-x, when the erasure must be controlled and
+specific to the prompt, such as when a named artistic style
+should be erased. On the other hand, fine-tuning of the unconditional layers (non-cross-attention modules), ESD-u, occurs when the erasure is required to be independent of the text in the
+prompt, such as when the global concept of NSFW nudity
+should be erased.
+
+\begin{discussion*}
+It seems like if we erase a specific concept like ``firefighters are predominately male," we would want to fine-tune the cross-attention layer ESD-x so as to not affect the general image output. \\
+
+On the other hand, if we are to erase larger-scale concepts like gender, we will need to be careful that this erasure does not interfere with other generated outputs that may not pertain to gender bias.
+\end{discussion*}
+
+\newpage
+
 \section{Summary of Work So Far}
@@
 RetinaFace, YOLO5Face).
+\\
+
+In our project, we use YOLOv8-face, which is an extension of the YOLOv8 object detector fine-tuned on the WIDER FACE dataset.
+
+\newpage
+
+\section{Presentation Notes}
+
+\noindent
+Let $C_i$ be the confidence the $i^{\text{th}}$ person (in a batch of images or in a single image) is male. \\
+
+\begin{definition}[Fairness Loss]\noindent The \textbf{fairness loss} is \[ \left( \frac{\sum\limits_i C_i}{\text{\# people}} - 0.5 \right)^2.\]
+\textit{The goal of this ``loss" is to get the average probability a person is male to be around 0.5, which mitigates the gender bias.}
+\end{definition}
+
+\begin{definition}[Confidence Loss]
+\noindent The \textbf{confidence loss} is \[ \frac{\alpha}{\text{\# people}} \sum_i -(C_i - 0.5)^2.\]
+\textit{The goal of this ``loss" is to get individuals to be distinctly male or female.}
+\end{definition}
 

### 2023-07-14 Notes/meeting_notes.tex
Added Day 39.

@@
 \title{UMD Fairness Research Group Meeting Notes}
-\author{David Yang$^{\dagger}$, Selena She$^{\dagger}$, Amy Feng$^{\dagger}$, Alexander Goslin$^{\dagger}$}
+\author{David Yang}
 \date{Summer 2023}
@@
 
-Datapoints from different datasets confer different distributions. Distribution Shift
+Datapoints from different datasets confer different distributions, which is the idea behind Distribution Shifts. \\
 
-In classic DA, source and target data are referenced at the same time.
+In classic DA (Domain Adaptation), the source and target data are referenced at the same time.
 This cross reference may cause privacy leaks, and so a better way is to keep data local.
@@
 In source-free DA, source and target data are referenced separately (first, models are trained on source domains and then it is passed to the target domain).
+See below for the classic DA Setup:
+
+\includegraphics[scale = 0.25]{ClassicDA_Setup.jpg}
 
@@
 Three types of pseudo label methods include hidden structure based, data augmentation based, and knowledge distillation based.
+\\
+
+\section{Diverse Reinforcement Learning}
+
+\textit{Led by Pankayaraj Pathmanathan.} \\
+
+\begin{definition}[Diverse RL]
+    Diverse RL aims to induce diversity in policies as well as online adapation of the diverse policies. 
+\end{definition}
+
+\underline{Problem Formulation: Inducing Diversity}: We want to generate multiple policies so that each policy will be different from each other.
+Related/previous work includes information based and successor feature based methods.\\
+
+Pan then presents his own ideal method for Diverse RL (details left out, to be presented in future papers). Flaws of previous objective functions include that
+\begin{enumerate}
+    \item It makes the support for a certain policy weaker.
+    \item It adds a level of stochasticity to the overall reward.
+\end{enumerate}
+
+He introduces an alternative stable objective function that can be intrepreted as a cross entropy between two distributions with a constant difference.
+The new objective will be without an indicator function term.
+With this objective, the stability factor is a bigger factor when it comes to training (even compared to ``ideal'' objectives).
 \end{document}
